Economic Theory of Fertility Explains Modern Natural Selection

### 2020-11-13 why-negative-selection.Rmd
p.value to p in graphs

  dfr %>% mutate(
          !! score_col := pretty_names(!! score_col),
          !! score_col := fct_reorder(!! score_col, estimate, order_abs(order_idx))
        ) %>% 
        ggplot(aes(estimate, {{score_col}}, fill = {{fill_col}}, ...,
          colour = p.value < 0.05/{{n_regs}})) +
          pval_geom_point() +
          my_vline + 
          pval_scale() +
          my_fill_scale(n = n_cats) +
          my_labs() +
          my_theme()
}

@@

res_edu %>% 
      mutate(
        term = pretty_names(term), 
        term = fct_reorder(term, estimate, order_abs(1)),
        "Age left FTE" = fct_relevel(age_fte_cat, "< 16", "16-18", "> 18"),
        "Age left FTE" = add_n(`Age left FTE`, "age_fte_cat")
      ) %>% 
      ggplot(aes(y = term, x = estimate, colour = p.value < 0.05/{{n_regs}}, 
        fill = `Age left FTE`)) +
        my_vline +
        pval_geom_point() + 
        pval_scale() +
        my_fill_scale(n = 3, direction = -1) +
        my_labs() +
        my_theme()

@@

n_regs <- as.double(nrow(res_income))
res_income %>% 
      mutate(
        term = pretty_names(term), 
        term = fct_reorder(term, estimate, order_abs(1)),
        Income = factor(income_cat, 
          labels = c("< £18K", "£18-30K", "£31-51K", "£52-100K", "> £100K")
        ),
        Income = add_n(Income, "income_cat")
      ) %>% 
      ggplot(aes(y = term, x = estimate, fill = Income, 
        colour = p.value < 0.05/{{n_regs}})) +
        my_vline +
        pval_geom_point(alpha = 0.8) + 
        my_fill_scale(n = 5, direction = -1) +
        pval_scale() +
        my_labs() +
        my_theme()     
```

@@

drake::loadd(res_partners)
res_partners %<>%       
      filter(grepl(":", term)) %>% 
      mutate(`N partners` = ifelse(grepl("TRUE:", term), "<= 3", "> 3"))

n_regs <- as.double(nrow(res_partners))
res_partners %>% 
      mutate(
        score_name = pretty_names(score_name)
      ) %>% 
      ggplot(aes(
        y      = reorder_within(score_name, estimate, sex, fun = order_abs(1)), 
        x      = estimate, 
        fill   = `N partners`, 
        colour = p.value < 0.05/{{n_regs}}
      )) + 
        my_vline +
        pval_geom_point() +
        facet_wrap(vars(sex), scales = "free_y") +
        my_fill_scale(n = 2) +
        pval_scale() +
        my_theme(legend.position = "bottom") +
        my_labs(x = "", y = "") + 
        scale_y_reordered()

@@

res_age_flb_cross %>% 
      mutate(
        score_name = pretty_names(score_name),
        score_name = fct_reorder(score_name, estimate, order_abs(1)),
        term       = gsub("age_flb_cat(.*):.*", "\\1", term),
        term       = add_n(term, "age_flb_cat")
      ) %>% 
      ggplot(aes(estimate, score_name, fill = term, 
        colour = p.value < 0.05/{{n_regs}})) +
        my_vline +
        pval_geom_point() +
        pval_scale() +
        my_fill_scale(n = 3, direction = -1, 
          guide = guide_legend(title = "Age at first live birth")) +
        my_labs() +
        my_theme()
```

@@

res_sex %>% 
      mutate(
        term = pretty_names(term),
      ) %>% 
      ggplot(aes(y = term, x = estimate, fill = sex, 
            colour = p.value < 0.05/{{n_regs}})) +
        my_vline +
        geom_linerange(data = res_sex_wide, 
          aes(
            y      = term,
            x      = NULL,
            fill   = NULL,
            xmin   = min_est, 
            xmax   = max_est, 
            colour = diff.p.value < 0.05/{{n_regs}}
          ), 
        group = "") +
        pval_geom_point() +
        pval_scale() +
        my_fill_scale(n = 2) +
        my_labs() +
        my_theme()

@@

res_combined %>% 
      mutate(
        score_name = pretty_names(score_name),
        score_name = fct_reorder(score_name, estimate, order_abs(2)),
        Regression = ifelse(reg.type == "raw", "Bivariate", "Controlled for AFLB")
      ) %>% 
      ggplot(aes(y = score_name, x = estimate, fill = Regression, 
        color = p.value < 0.05/{{n_regs}})) + 
        geom_vline(xintercept = 0, linetype = "dashed", color = "grey20") +
        pval_geom_point() +
        pval_scale() +
        scale_fill_brewer(type = "qual", palette = 3) +
        my_labs() +
        my_theme()
```

@@

n_regs <- length(score_names)
res_wt_combined %>% 
  mutate(
    Weights  = fct_relevel(Weights, "Geographical", "Age/Qualification",
                "Age/Qual/AFLB", "None"),
    term     = pretty_names(term),
    term     = fct_reorder(term, estimate, order_abs(1))
  ) %>% 
  ggplot(aes(x = estimate, y = term, shape = Weights, fill = Weights, colour = p.value < 0.05/{{n_regs}})) +
  geom_point(size = 1.5, stroke = 0.5) +
  my_vline +
  pval_scale() +
  scale_fill_manual(values = c(
    "None"              = "grey15", 
    "Geographical"      = "dodgerblue4",
    "Age/Qualification" = "steelblue2",
    "Age/Qual/AFLB"      = "darkseagreen4"
  )) +
  scale_shape_manual(values = c(
    "None" = "square filled", 
    "Geographical" = "circle filled",
    "Age/Qualification" = "circle filled", 
    "Age/Qual/AFLB" = "circle filled"
  ))

@@

n_regs <- as.double(nrow(res_all))
res_all %>% 
      mutate(
        term    = pretty_names(term),
        term    = reorder_within(term, estimate, dep.var, order_abs(1)),
        dep.var = fct_inorder(dep.var) 
      ) %>% 
      ggplot(aes(y = term, x = estimate, fill = reg.type, 
        colour = p.value < 0.05/{{n_regs}})) +
        my_vline + 
        facet_wrap(vars(dep.var), scales = "free_y") +
        pval_geom_point(position = position_dodge(0.4)) +
        my_labs() +
        pval_scale() +
        my_fill_scale(n = 2, guide = guide_legend(title = "")) +
        my_theme() +
        scale_y_reordered()

@@

res_pcs %>% 
      mutate(
        estimate = abs(estimate),
        dep.var  = fct_relevel(dep.var, "N children")
      ) %>% 
      ggplot(aes(estimate, dep.var, colour = p.value < 0.05/{{n_regs}})) + 
        geom_jitter(height = 0.15, width = 0, alpha = 0.9) + 
        scale_x_log10(labels = scales::label_number(accuracy = 0.0001)) +
        labs(x = "Effect size (log scale)", y = "") + 
        pval_scale(aesthetics = "colour")

@@

n_regs <- as.double(nrow(res_partners_controlled))
res_partners_controlled %>% 
      mutate(
        score_name = pretty_names(score_name)
      ) %>% 
      ggplot(aes(
        y      = reorder_within(score_name, estimate, sex, fun = order_abs(1)), 
        x      = estimate, 
        fill   = `N partners`, 
        colour = p.value < 0.05/{{n_regs}}
      )) + 
        my_vline +
        pval_geom_point() +
        facet_wrap(vars(sex), scales = "free_y") +
        my_fill_scale(n = 2) +
        pval_scale() +
        my_theme(legend.position = "bottom") +
        my_labs(x = "", y = "") + 
        scale_y_reordered()

@@

res_age_birth_parents %>% 
    filter(! term %in% c("fath_age_birth", "moth_age_birth")) %>% 
    mutate(
      term    = pretty_names(term),
      term    = fct_reorder(term, estimate, order_abs(2)),
      Control = ifelse(control == "fath_age_birth", 
                  "Father's age at birth", 
                  "Mother's age at birth"
                )
    ) %>% 
    ggplot(aes(y = term, x = estimate, fill = Control, 
      colour = p.value < 0.05/{{n_regs}})) + 
      pval_geom_point(alpha = 0.8) +  
      my_vline +
      my_fill_scale(2) +
      pval_scale() +
      my_labs()

@@

res_age_flb_dv %>% 
      mutate(
        term = pretty_names(term),
        term = fct_reorder(term, estimate, order_abs(1))
      ) %>% 
      ggplot(aes(estimate, term, colour = p.value < 0.05 / {{n_regs}})) + 
      my_vline +
      pval_geom_point(fill = "steelblue4") +
      pval_scale() + 
      my_labs() +
      my_theme()

@@

res_age_birth_parents_dv %>% 
      mutate(
        term = pretty_names(term),
        term = fct_reorder(term, estimate, order_abs(1)),
        "Dependent variable" = dplyr::recode(dep.var, 
          "fath_age_birth" = "Father's age", 
          "moth_age_birth" = "Mother's age"
        )
      ) %>% 
      ggplot(aes(estimate, term, fill = `Dependent variable`, 
        colour = p.value < 0.05 / {{n_regs}})) + 
        my_vline +
        pval_geom_point() +
        pval_scale() +
        my_fill_scale(n = 2) +
        my_labs()

@@

loadd(res_together)
n_regs <- as.double(nrow(res_together))
res_together %>% 
      mutate(
        term = pretty_names(term),
        dep.var = dplyr::recode(dep.var, 
          "n_children" = "N Children", "n_sibs" = "N Siblings"),
        dep.var = fct_relevel(dep.var, "N Siblings")
      ) %>% 
      ggplot(aes(y = reorder_within(term, estimate, dep.var, order_abs(1)), 
        x = estimate, color = p.value < 0.05/{{n_regs}}, fill  = PCs)) + 
        pval_geom_point(alpha = 0.8) +
        my_vline +
        facet_wrap(vars(dep.var), scales = "free_y") +
        pval_scale() +
        my_fill_scale(n = 2) +
        my_labs() + 
        scale_y_reordered() +
        theme(legend.position = "bottom")
```

>>>>

  dfr %>% mutate(
          !! score_col := pretty_names(!! score_col),
          !! score_col := fct_reorder(!! score_col, estimate, order_abs(order_idx))
        ) %>% 
        rename(p = p.value) %>% 
        ggplot(aes(estimate, {{score_col}}, fill = {{fill_col}}, ...,
          colour = p < 0.05/{{n_regs}})) +
          pval_geom_point() +
          my_vline + 
          pval_scale() +
          my_fill_scale(n = n_cats) +
          my_labs() +
          my_theme()
}

@@

res_edu %>% 
      mutate(
        term = pretty_names(term), 
        term = fct_reorder(term, estimate, order_abs(1)),
        "Age left FTE" = fct_relevel(age_fte_cat, "< 16", "16-18", "> 18"),
        "Age left FTE" = add_n(`Age left FTE`, "age_fte_cat")
      ) %>% 
      rename(p = p.value) %>% 
      ggplot(aes(y = term, x = estimate, colour = p < 0.05/{{n_regs}}, 
        fill = `Age left FTE`)) +
        my_vline +
        pval_geom_point() + 
        pval_scale() +
        my_fill_scale(n = 3, direction = -1) +
        my_labs() +
        my_theme()

@@

n_regs <- as.double(nrow(res_income))
res_income %>% 
      mutate(
        term = pretty_names(term), 
        term = fct_reorder(term, estimate, order_abs(1)),
        Income = factor(income_cat, 
          labels = c("< £18K", "£18-30K", "£31-51K", "£52-100K", "> £100K")
        ),
        Income = add_n(Income, "income_cat")
      ) %>% 
      rename(p = p.value) %>% 
      ggplot(aes(y = term, x = estimate, fill = Income, 
        colour = p < 0.05/{{n_regs}})) +
        my_vline +
        pval_geom_point(alpha = 0.8) + 
        my_fill_scale(n = 5, direction = -1) +
        pval_scale() +
        my_labs() +
        my_theme()     
```

@@

drake::loadd(res_partners)
res_partners %<>%       
      filter(grepl(":", term)) %>% 
      mutate(`N partners` = ifelse(grepl("TRUE:", term), "3 or less", "4 or more"))

n_regs <- as.double(nrow(res_partners))
res_partners %>% 
      mutate(
        score_name = pretty_names(score_name)
      ) %>% 
      rename(p = p.value) %>% 
      ggplot(aes(
        y      = reorder_within(score_name, estimate, sex, fun = order_abs(1)), 
        x      = estimate, 
        fill   = `N partners`, 
        colour = p < 0.05/{{n_regs}}
      )) + 
        my_vline +
        pval_geom_point() +
        facet_wrap(vars(sex), scales = "free_y") +
        my_fill_scale(n = 2) +
        pval_scale() +
        my_theme(legend.position = "bottom") +
        my_labs(x = "", y = "") + 
        scale_y_reordered()

@@

res_age_flb_cross %>% 
      mutate(
        score_name = pretty_names(score_name),
        score_name = fct_reorder(score_name, estimate, order_abs(1)),
        term       = gsub("age_flb_cat(.*):.*", "\\1", term),
        term       = add_n(term, "age_flb_cat")
      ) %>% 
      rename(p = p.value) %>% 
      ggplot(aes(estimate, score_name, fill = term, 
        colour = p < 0.05/{{n_regs}})) +
        my_vline +
        pval_geom_point() +
        pval_scale() +
        my_fill_scale(n = 3, direction = -1, 
          guide = guide_legend(title = "Age at first live birth")) +
        my_labs() +
        my_theme()
```

@@

res_sex %>% 
      mutate(
        term = pretty_names(term),
      ) %>% 
      rename(p = p.value) %>% 
      ggplot(aes(y = term, x = estimate, fill = sex, 
            colour = p < 0.05/{{n_regs}})) +
        my_vline +
        geom_linerange(data = res_sex_wide, 
          aes(
            y      = term,
            x      = NULL,
            fill   = NULL,
            xmin   = min_est, 
            xmax   = max_est, 
            colour = diff.p.value < 0.05/{{n_regs}}
          ), 
        group = "") +
        pval_geom_point() +
        pval_scale() +
        my_fill_scale(n = 2) +
        my_labs() +
        my_theme()

@@

res_combined %>% 
      mutate(
        score_name = pretty_names(score_name),
        score_name = fct_reorder(score_name, estimate, order_abs(2)),
        Regression = ifelse(reg.type == "raw", "Bivariate", "Controlled for AFLB")
      ) %>% 
      rename(p = p.value) %>% 
      ggplot(aes(y = score_name, x = estimate, fill = Regression, 
        color = p < 0.05/{{n_regs}})) + 
        geom_vline(xintercept = 0, linetype = "dashed", color = "grey20") +
        pval_geom_point() +
        pval_scale() +
        scale_fill_brewer(type = "qual", palette = 3) +
        my_labs() +
        my_theme()
```

@@

n_regs <- length(score_names)
res_wt_combined %>% 
  mutate(
    Weights  = fct_relevel(Weights, "Geographical", "Age/Qualification",
                "Age/Qual/AFLB", "None"),
    term     = pretty_names(term),
    term     = fct_reorder(term, estimate, order_abs(1))
  ) %>% 
  rename(p = p.value) %>% 
  ggplot(aes(
    x = estimate, 
    y = term, 
    shape = Weights, 
    fill = Weights, 
    colour = p < 0.05/{{n_regs}}
  )) +
  geom_point(size = 1.5, stroke = 0.5) +
  my_vline +
  pval_scale() +
  scale_fill_manual(values = c(
    "None"              = "grey15", 
    "Geographical"      = "dodgerblue4",
    "Age/Qualification" = "steelblue2",
    "Age/Qual/AFLB"      = "darkseagreen4"
  )) +
  scale_shape_manual(values = c(
    "None" = "square filled", 
    "Geographical" = "circle filled",
    "Age/Qualification" = "circle filled", 
    "Age/Qual/AFLB" = "circle filled"
  ))

@@

n_regs <- as.double(nrow(res_all))
res_all %>% 
      mutate(
        term    = pretty_names(term),
        term    = reorder_within(term, estimate, dep.var, order_abs(1)),
        dep.var = fct_inorder(dep.var) 
      ) %>% 
      rename(p = p.value) %>% 
      ggplot(aes(y = term, x = estimate, fill = reg.type, 
        colour = p < 0.05/{{n_regs}})) +
        my_vline + 
        facet_wrap(vars(dep.var), scales = "free_y") +
        pval_geom_point(position = position_dodge(0.4)) +
        my_labs() +
        pval_scale() +
        my_fill_scale(n = 2, guide = guide_legend(title = "")) +
        my_theme() +
        scale_y_reordered()

@@

res_pcs %>% 
      mutate(
        estimate = abs(estimate),
        dep.var  = fct_relevel(dep.var, "N children")
      ) %>% 
      rename(p = p.value) %>% 
      ggplot(aes(estimate, dep.var, colour = p < 0.05/{{n_regs}})) + 
        geom_jitter(height = 0.15, width = 0, alpha = 0.9) + 
        scale_x_log10(labels = scales::label_number(accuracy = 0.0001)) +
        labs(x = "Effect size (log scale)", y = "") + 
        pval_scale(aesthetics = "colour")

@@

n_regs <- as.double(nrow(res_partners_controlled))
res_partners_controlled %>% 
      mutate(
        score_name = pretty_names(score_name)
      ) %>% 
      rename(p = p.value) %>% 
      ggplot(aes(
        y      = reorder_within(score_name, estimate, sex, fun = order_abs(1)), 
        x      = estimate, 
        fill   = `N partners`, 
        colour = p < 0.05/{{n_regs}}
      )) + 
        my_vline +
        pval_geom_point() +
        facet_wrap(vars(sex), scales = "free_y") +
        my_fill_scale(n = 2) +
        pval_scale() +
        my_theme(legend.position = "bottom") +
        my_labs(x = "", y = "") + 
        scale_y_reordered()

@@

res_age_birth_parents %>% 
    filter(! term %in% c("fath_age_birth", "moth_age_birth")) %>% 
    mutate(
      term    = pretty_names(term),
      term    = fct_reorder(term, estimate, order_abs(2)),
      Control = ifelse(control == "fath_age_birth", 
                  "Father's age at birth", 
                  "Mother's age at birth"
                )
    ) %>% 
    rename(p = p.value) %>% 
    ggplot(aes(y = term, x = estimate, fill = Control, 
      colour = p < 0.05/{{n_regs}})) + 
      pval_geom_point(alpha = 0.8) +  
      my_vline +
      my_fill_scale(2) +
      pval_scale() +
      my_labs()

@@

res_age_flb_dv %>% 
      mutate(
        term = pretty_names(term),
        term = fct_reorder(term, estimate, order_abs(1))
      ) %>% 
      rename(p = p.value) %>% 
      ggplot(aes(estimate, term, colour = p < 0.05 / {{n_regs}})) + 
      my_vline +
      pval_geom_point(fill = "steelblue4") +
      pval_scale() + 
      my_labs() +
      my_theme()

@@

res_age_birth_parents_dv %>% 
      mutate(
        term = pretty_names(term),
        term = fct_reorder(term, estimate, order_abs(1)),
        "Dependent variable" = dplyr::recode(dep.var, 
          "fath_age_birth" = "Father's age", 
          "moth_age_birth" = "Mother's age"
        )
      ) %>% 
      rename(p = p.value) %>% 
      ggplot(aes(estimate, term, fill = `Dependent variable`, 
        colour = p < 0.05 / {{n_regs}})) + 
        my_vline +
        pval_geom_point() +
        pval_scale() +
        my_fill_scale(n = 2) +
        my_labs()

@@

loadd(res_together)
n_regs <- as.double(nrow(res_together))
res_together %>% 
      mutate(
        term = pretty_names(term),
        dep.var = dplyr::recode(dep.var, 
          "n_children" = "N Children", "n_sibs" = "N Siblings"),
        dep.var = fct_relevel(dep.var, "N Siblings")
      ) %>% 
      rename(p = p.value) %>% 
      ggplot(aes(y = reorder_within(term, estimate, dep.var, order_abs(1)), 
        x = estimate, color = p < 0.05/{{n_regs}}, fill  = PCs)) + 
        pval_geom_point(alpha = 0.8) +
        my_vline +
        facet_wrap(vars(dep.var), scales = "free_y") +
        pval_scale() +
        my_fill_scale(n = 2) +
        my_labs() + 
        scale_y_reordered() +
        theme(legend.position = "bottom")
```
